Legion: Expressing Locality and Independence with Logical Regions

### 2012-06-25 doc/sc2012/legion.tex
thanks

\bibliographystyle{IEEEtran}
\usepackage{amsmath,amsthm}
\usepackage{listings}
\usepackage{tikz}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{booktabs}
\usepackage{dcolumn}
\usepackage{cancel}
\usepackage{graphics}

\newcommand{\infrule}[2]{\displaystyle\frac{\displaystyle\strut{#1}}{\displaystyle\strut {#2}}}
\newcommand{\deref}{\ast}
\newcommand{\rread}[1]{\mbox{\em Read}(#1)}
\newcommand{\rwrite}[1]{\mbox{\em Write}(#1)}
\newcommand{\lca}[2]{#1 \sqcup #2}
\newcommand{\rleq}{\leq}
\newcommand{\interval}[1]{\mbox{\em interval}(#1)}
\newcommand{\context}[1]{\mbox{\em context}(#1)}
\newtheorem{theorem}{Theorem} 
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{observation}[theorem]{Observation}

@@

\title{Legion: Expressing Locality and Independence with Logical Regions\thanks{This work was supported by the Army High Performance Research Center, DARPA contract HR0011-10-9-0008, and NVIDIA.  The views and conclusions contained in this document are those of the authors and should not be interpreted as representing the official policies, either expressed or implied, of the U.S. Government.}}
\author{
\IEEEauthorblockN{Michael Bauer\IEEEauthorrefmark{1},
%\authorinfo(Stanford University, email: \mbox{mebauer@cs.stanford.edu}
Sean Treichler\IEEEauthorrefmark{1}, 
%\authorinfo(Stanford University, email: \mbox{sjt@cs.stanford.edu}
Elliott Slaughter\IEEEauthorrefmark{1}, 
% \authorinfo(Stanford University, email: \mbox{slaughter@cs.stanford.edu}
Alex Aiken\IEEEauthorrefmark{1}  
%\authorinfo(Stanford University, email: \mbox{aiken@cs.stanford.edu}
%\email{aiken@cs.stanford.edu}
}
\IEEEauthorblockA{
\IEEEauthorrefmark{1}{Computer Science Department, Stanford University}
}
}

@@

Logical regions do not commit to any particular layout of the data or
placement in the machine.  At runtime, each logical region has one or
more {\em physical instances} assigned to specific memories .  It is often useful to have multiple
physical instances of a logical region (e.g., to replicate read-only data, or to allow
independent reductions that are later combined).

>>>>

\bibliographystyle{IEEEtran}
\usepackage{amsmath,amsthm}
\usepackage{listings}
\usepackage{tikz}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{booktabs}
\usepackage{dcolumn}
\usepackage{cancel}
\usepackage{graphics}
\usepackage{url}

\newcommand{\infrule}[2]{\displaystyle\frac{\displaystyle\strut{#1}}{\displaystyle\strut {#2}}}
\newcommand{\deref}{\ast}
\newcommand{\rread}[1]{\mbox{\em Read}(#1)}
\newcommand{\rwrite}[1]{\mbox{\em Write}(#1)}
\newcommand{\lca}[2]{#1 \sqcup #2}
\newcommand{\rleq}{\leq}
\newcommand{\interval}[1]{\mbox{\em interval}(#1)}
\newcommand{\context}[1]{\mbox{\em context}(#1)}
\newtheorem{theorem}{Theorem} 
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{observation}[theorem]{Observation}
\IEEEoverridecommandlockouts

@@

\title{Legion: Expressing Locality and Independence with Logical
  Regions\thanks{This work was supported by the Army High Performance
    Research Center (DARPA contract HR0011-10-9-0008), a subcontract
    from Los Alamos National Laboratory for the DOE Office of Science,
    Advanced Scientific Computing Research, and NVIDIA.  The views and
    conclusions contained in this document are those of the authors
    and should not be interpreted as representing the official
    policies, either expressed or implied, of the U.S. Government.}}
\author{ \IEEEauthorblockN{Michael Bauer\IEEEauthorrefmark{1},
%\authorinfo(Stanford University, email: \mbox{mebauer@cs.stanford.edu}
Sean Treichler\IEEEauthorrefmark{1}, 
%\authorinfo(Stanford University, email: \mbox{sjt@cs.stanford.edu}
Elliott Slaughter\IEEEauthorrefmark{1}, 
% \authorinfo(Stanford University, email: \mbox{slaughter@cs.stanford.edu}
Alex Aiken\IEEEauthorrefmark{1}  
%\authorinfo(Stanford University, email: \mbox{aiken@cs.stanford.edu}
%\email{aiken@cs.stanford.edu}
}
\IEEEauthorblockA{
\IEEEauthorrefmark{1}{Computer Science Department, Stanford University}
}
}

@@

Logical regions do not commit to any particular layout of the data or
placement in the machine.  At runtime, each logical region has one or
more {\em physical instances} assigned to specific memories.  It is often useful to have multiple
physical instances of a logical region (e.g., to replicate read-only data, or to allow
independent reductions that are later combined).
